---
title: "INTIS (INTENT Insights)"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

<style>
body {
    font-size: 14px;
}
</style>

```{r setup, include=FALSE}
# Load the necessary packages
pacman::p_load(tidyverse, flexdashboard, shiny, readxl, tmap, DT, leaflet)
data("World")

# Function for wrangling the Excel file
vol_df <- function(df, year, vol) {
  df_out <- df %>%
    group_by(Year, Volume) %>%
    filter(Year == year && Volume == vol)
  df_out <- rbind(
    cbind(df_out$Artist1, df_out$Country1),
    cbind(df_out$Artist2, df_out$Country2),
    cbind(df_out$Artist3, df_out$Country3),
    cbind(df_out$Artist4, df_out$Country4),
    cbind(df_out$Artist5, df_out$Country5),
    cbind(df_out$Artist6, df_out$Country6),
    cbind(df_out$Artist7, df_out$Country7)
  ) %>%
    na.omit() %>%
    as.data.frame()
  colnames(df_out) <- c("Artist", "Country")
  return(df_out)
}

# Function for forming links
createLink <- function(val) {
  val1 <- gsub(" ", "+", val)
  sprintf('<a href="https://www.google.com/search?as_epq=%s" target="_blank">%s</a>', val1, val)
}

# Function for mode
getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}

# Load the file
df <- read_excel("INTIS.xlsx")

# Prepare data for INTENT 2020
v2020_1 <- vol_df(df, 2020, 1)
v2020_2 <- vol_df(df, 2020, 2)
v2020_3 <- vol_df(df, 2020, 3)
v2020 <- rbind(v2020_1, v2020_2, v2020_3) %>% as.data.frame()
v2020_artists <- unique(v2020$Artist)
v2020_country <- table(v2020$Country) %>% as.data.frame()

# Prepare data for INTENT 2021
v2021_1 <- vol_df(df, 2021, 1)
v2021_2 <- vol_df(df, 2021, 2)
v2021_3 <- vol_df(df, 2021, 3)
v2021_4 <- vol_df(df, 2021, 4)
v2021_5 <- vol_df(df, 2021, 5)
v2021_6 <- vol_df(df, 2021, 6)
v2021 <- rbind(v2021_1, v2021_2, v2021_3, v2021_4, v2021_5, v2021_6) %>% as.data.frame()
v2021_artists <- unique(v2021$Artist)
v2021_country <- table(v2021$Country) %>% as.data.frame()

# Prepare data for INTENT 2022
v2022_1 <- vol_df(df, 2022, 1)
v2022_2 <- vol_df(df, 2022, 2)
v2022_3 <- vol_df(df, 2022, 3)
v2022_4 <- vol_df(df, 2022, 4)
v2022_5 <- vol_df(df, 2022, 5)
v2022_6 <- vol_df(df, 2022, 6)
v2022 <- rbind(v2022_1, v2022_2, v2022_3, v2022_4, v2022_5, v2022_6) %>% as.data.frame()
v2022_artists <- unique(v2022$Artist)
v2022_country <- table(v2022$Country) %>% as.data.frame()
```

# Overview

## Column {data-width="650"}

### Contributing Countries

```{r}
# Prepare data for overview
v_artists <- c(v2020_artists, v2021_artists, v2022_artists) %>%
  unique() %>%
  sort()
v_total <- rbind(v2020, v2021, v2022) %>% as.data.frame()
v_country <- table(v_total$Country) %>% as.data.frame()
colnames(v_country) <- c("name", "TotalContributions")

# Prepare the map
ContributingCountries <- inner_join(World, v_country, by = "name") %>% select(-iso_a3)
for (i in 1:nrow(ContributingCountries)) {
  v_t <- v_total %>%
    filter(Country == as.character(ContributingCountries$name[i])) %>%
    unique()
  v_t <- paste(sort(v_t$Artist), collapse = "<br>")
  ContributingCountries$Artists[i] <- v_t
}

# Show the map
tmap_mode("view")
tm_shape(ContributingCountries) + tm_polygons("TotalContributions",
  popup.vars = c("Artists", "TotalContributions"),
  popup.format = list("html.escape" = FALSE)
) +
  tm_style("white") + tm_view(set.view = c(7, 51, 4))
```

## Column {data-width="350"}

### Artist Discovery

```{r}
# Show the artist list
v_artists <- v_artists %>%
  createLink() %>%
  as.data.frame()
colnames(v_artists) <- ""
DT::datatable(v_artists,
  rownames = FALSE, options = list(
    pageLength = 3,
    scrollX = FALSE,
    dom = "tip"
  ),
  class = "white-space: nowrap",
  escape = FALSE, selection = "single"
)
```

### Descriptive Statistics

```{r}
# Show the descriptive statistics
descStats <- rbind(
  c("Total contributions:", nrow(v_total)),
  c("Total artists:", nrow(v_artists)),
  c("Total countries:", nrow(v_country)),
  c("Top artist:", getmode(v_total$Artist)),
  c("Top country:", getmode(v_total$Country))
) %>% as.data.frame()

# Hides header
headerCallback <- c(
  "function(thead, data, start, end, display){",
  "  $('th', thead).css('display', 'none');",
  "}"
)

DT::datatable(descStats,
  rownames = FALSE,
  options = list(
    pageLength = 5,
    scrollX = FALSE,
    dom = "t",
    headerCallback = JS(headerCallback)
  ),
  class = "white-space: nowrap",
  escape = FALSE, selection = "none"
)
```

# Description {.sidebar}

The INTIS (INTENT Insights) dashboard provides data visualization of the distribution of contributing artists according to their countries of origin. If you click on a country's outline, you will be able to see information about artists from that country who have contributed, as well as the total number of contributions from the country. The totals for contributions, artists, countries, and modes for artists and countries (top artist/country) are provided as well. The presence of international collaborations results in a slightly higher number of contributions than the total number of tracks; for example, one track featuring two artists from different countries counts as two contributions.

The data is available for the whole project as well as for the separate installments. INTIS also allows you to research the artists further; by clicking on the artist name in the Artist Discovery field, you will be able to see the results of a Google search on the artist name.

# INTENT 2020 {data-navmenu="Installments"}

## Column {data-width="650"}

### Contributing Countries (INTENT 2020)

```{r}
# Prepare data for overview
v_artists20 <- v2020_artists %>%
  unique() %>%
  sort()
v_total20 <- rbind(v2020) %>% as.data.frame()
v_country20 <- table(v_total20$Country) %>% as.data.frame()
colnames(v_country20) <- c("name", "TotalContributions")

# Prepare the map
ContributingCountries20 <- inner_join(World, v_country20, by = "name") %>% select(-iso_a3)
for (i in 1:nrow(ContributingCountries20)) {
  v_t <- v_total20 %>%
    filter(Country == as.character(ContributingCountries20$name[i])) %>%
    unique()
  v_t <- paste(sort(v_t$Artist), collapse = "<br>")
  ContributingCountries20$Artists[i] <- v_t
}

# Show the map
tmap_mode("view")
tm_shape(ContributingCountries20) + tm_polygons("TotalContributions",
  popup.vars = c("Artists", "TotalContributions"),
  popup.format = list("html.escape" = FALSE)
) +
  tm_style("white") + tm_view(set.view = c(7, 51, 4))
```

## Column {data-width="350"}

### Artist Discovery (INTENT 2020)

```{r}
# Show the artist list
v_artists20 <- v_artists20 %>%
  createLink() %>%
  as.data.frame()
colnames(v_artists20) <- ""
DT::datatable(v_artists20,
  rownames = FALSE, options = list(
    pageLength = 3,
    scrollX = FALSE,
    dom = "tip"
  ),
  class = "white-space: nowrap",
  escape = FALSE, selection = "single"
)
```

### Descriptive Statistics (INTENT 2020)

```{r}
# Show the descriptive statistics
descStats20 <- rbind(
  c("Total contributions:", nrow(v_total20)),
  c("Total artists:", nrow(v_artists20)),
  c("Total countries:", nrow(v_country20)),
  c("Top artist:", getmode(v_total20$Artist)),
  c("Top country:", getmode(v_total20$Country))
) %>% as.data.frame()

# Hides header
headerCallback <- c(
  "function(thead, data, start, end, display){",
  "  $('th', thead).css('display', 'none');",
  "}"
)

DT::datatable(descStats20,
  rownames = FALSE,
  options = list(
    pageLength = 5,
    scrollX = FALSE,
    dom = "t",
    headerCallback = JS(headerCallback)
  ),
  class = "white-space: nowrap",
  escape = FALSE, selection = "none"
)
```

# INTENT 2021 {data-navmenu="Installments"}

## Column {data-width="650"}

### Contributing Countries (INTENT 2021)

```{r}
# Prepare data for overview
v_artists21 <- v2021_artists %>%
  unique() %>%
  sort()
v_total21 <- rbind(v2021) %>% as.data.frame()
v_country21 <- table(v_total21$Country) %>% as.data.frame()
colnames(v_country21) <- c("name", "TotalContributions")

# Prepare the map
ContributingCountries21 <- inner_join(World, v_country21, by = "name") %>% select(-iso_a3)
for (i in 1:nrow(ContributingCountries21)) {
  v_t <- v_total21 %>%
    filter(Country == as.character(ContributingCountries21$name[i])) %>%
    unique()
  v_t <- paste(sort(v_t$Artist), collapse = "<br>")
  ContributingCountries21$Artists[i] <- v_t
}

# Show the map
tmap_mode("view")
tm_shape(ContributingCountries21) + tm_polygons("TotalContributions",
  popup.vars = c("Artists", "TotalContributions"),
  popup.format = list("html.escape" = FALSE)
) +
  tm_style("white") + tm_view(set.view = c(7, 51, 4))
```

## Column {data-width="350"}

### Artist Discovery (INTENT 2021)

```{r}
# Show the artist list
v_artists21 <- v_artists21 %>%
  createLink() %>%
  as.data.frame()
colnames(v_artists21) <- ""
DT::datatable(v_artists21,
  rownames = FALSE, options = list(
    pageLength = 3,
    scrollX = FALSE,
    dom = "tip"
  ),
  class = "white-space: nowrap",
  escape = FALSE, selection = "single"
)
```

### Descriptive Statistics (INTENT 2021)

```{r}
# Show the descriptive statistics
descStats21 <- rbind(
  c("Total contributions:", nrow(v_total21)),
  c("Total artists:", nrow(v_artists21)),
  c("Total countries:", nrow(v_country21)),
  c("Top artist:", getmode(v_total21$Artist)),
  c("Top country:", getmode(v_total21$Country))
) %>% as.data.frame()

# Hides header
headerCallback <- c(
  "function(thead, data, start, end, display){",
  "  $('th', thead).css('display', 'none');",
  "}"
)

DT::datatable(descStats21,
  rownames = FALSE,
  options = list(
    pageLength = 5,
    scrollX = FALSE,
    dom = "t",
    headerCallback = JS(headerCallback)
  ),
  class = "white-space: nowrap",
  escape = FALSE, selection = "none"
)
```

# INTENT 2022 {data-navmenu="Installments"}

## Column {data-width="650"}

### Contributing Countries (INTENT 2022)

```{r}
# Prepare data for overview
v_artists22 <- v2022_artists %>%
  unique() %>%
  sort()
v_total22 <- rbind(v2022) %>% as.data.frame()
v_country22 <- table(v_total22$Country) %>% as.data.frame()
colnames(v_country22) <- c("name", "TotalContributions")

# Prepare the map
ContributingCountries22 <- inner_join(World, v_country22, by = "name") %>% select(-iso_a3)
for (i in 1:nrow(ContributingCountries22)) {
  v_t <- v_total22 %>%
    filter(Country == as.character(ContributingCountries22$name[i])) %>%
    unique()
  v_t <- paste(sort(v_t$Artist), collapse = "<br>")
  ContributingCountries22$Artists[i] <- v_t
}

# Show the map
tmap_mode("view")
tm_shape(ContributingCountries22) + tm_polygons("TotalContributions",
  popup.vars = c("Artists", "TotalContributions"),
  popup.format = list("html.escape" = FALSE)
) +
  tm_style("white") + tm_view(set.view = c(7, 51, 4))
```

## Column {data-width="350"}

### Artist Discovery (INTENT 2022)

```{r}
# Show the artist list
v_artists22 <- v_artists22 %>%
  createLink() %>%
  as.data.frame()
colnames(v_artists22) <- ""
DT::datatable(v_artists22,
  rownames = FALSE, options = list(
    pageLength = 3,
    scrollX = FALSE,
    dom = "tip"
  ),
  class = "white-space: nowrap",
  escape = FALSE, selection = "single"
)
```

### Descriptive Statistics (INTENT 2022)

```{r}
# Show the descriptive statistics
descStats22 <- rbind(
  c("Total contributions:", nrow(v_total22)),
  c("Total artists:", nrow(v_artists22)),
  c("Total countries:", nrow(v_country22)),
  c("Top artist:", getmode(v_total22$Artist)),
  c("Top country:", getmode(v_total22$Country))
) %>% as.data.frame()

# Hides header
headerCallback <- c(
  "function(thead, data, start, end, display){",
  "  $('th', thead).css('display', 'none');",
  "}"
)

DT::datatable(descStats22,
  rownames = FALSE,
  options = list(
    pageLength = 5,
    scrollX = FALSE,
    dom = "t",
    headerCallback = JS(headerCallback)
  ),
  class = "white-space: nowrap",
  escape = FALSE, selection = "none"
)
```
